%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Implémentation d’un workflow designer personnalisé}

\author{F}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{Diplôme National d'Ingénieur en Sciences Appliquées et Technologiques}
\speciality{Architecture IT Et Cloud Computing}
%\speciality{Génie des Télécommunications et Réseaux}
%\speciality{Génie Informatique des Systèmes Industriels}

%% Encadrant professionnel
\proFramerName{Mme.Nouhe Arbi}
\proFramerSpeciality{Manager}

%% Encadrant académique
\academicFramerName{Mr.Mohamed Selmène BEN YAHIA}
\academicFramerSpeciality{Maître Assistante}

%% Entreprise d'accueil
\companyName{Sofrecom}

%% Année universitaire
\collegeYear{2022 - 2023}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{J'autorise l'étudiante farah ben mahmoud à faire le dépôt de son rapport de stage en vue d'une soutenance.}

\academicSignSentence{J'autorise l'étudiante farah ben mahmoud à faire le dépôt de son rapport de stage en vue d'une soutenance.}

%%% AR
\arabicAbstract{ في إطار الحصول على شهادة الهندسة  في الاعلامية اختصاص هندسة البرمجيات ، قمنا بإعداد مشروع نهاية الدراسات داخل شركة "أدفيتيم". يتمثل المشروع  في العمل على جزء الشبكة الاجتماعية للمنتج من خلال تطبيق ثلاث ميزات جديدة: المحادثة ، تشفير الرسائل والإشعارات.
تمت إدارة  هذا المشروع عن طريق  سكروم و استعملنا سبرينغ بوت و أنجولار .
}
\arabicAbstractKeywords{ كورنتو،إشعارات،تشفير}

%% To use latin characters inside the arabic text
% just put them inside the command \textLR{}
%%%%

%%% FR
\frenchAbstract{Dans le cadre de l’obtention du diplôme d’ingénieur en  informatique spécialité génie logiciel , nous avons effectué un stage de fin d’études au sein d’Advyteam. Le projet consiste à travailler sur la partie réseau social  du produit Accretio en implémentant trois nouvelles fonctionnalités: chat peer to peer, chiffrement de la messagerie et notification en temps réel. En outre, nous avons suivi la méthode Scrum pour la gestion du projet ainsie que mes technologie spring boot et Angular.}

\frenchAbstractKeywords{Kurrento Media Server,openVidu-Browser,  temps réel , chiffrement ,Notifications , spring boot ,Angular }

%%% EN
\englishAbstract{As part of the graduation of computer engineer specialization in software engineering and information systems, we have accomplished to a graduation project within Advyteam.The project consists of working on the social network part of the product by implementing three new features: chat peer-to-peer , messaging encryption and real-time notification. In addition, we followed the Scrum method for our project management and we used spring boot and Angular as technology.}

\englishAbstractKeywords{
Kurrento Media Server,openVidu-Browser, real time ,encryption,notification , spring boot , Angular }

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
